Modal Verification Patterns for Systems

### 2025-06-25 paper.tex
handle a redundancy todo

\todo[inline,color=cyan]{the hybrid logic paragraph above is good, but this first paragraph about nominalization repeats
some of the same things. We should merge them.}
\paragraph{Nominalization}
Some classes of assertions benefit specifically from \emph{naming} the explicit conditions where they are true (as opposed to simply requiring them to be true \emph{somewhere} or \emph{everywhere} as in the most classic modal operators).
This naming generally resembles
the \emph{satisfaction} operator of 
\emph{hybrid logic}~\cite{blackburn1995hybrid,areces2001hybrid}: $@_\iota P$ which evaluates the truth of $P$ at the named (Kripke model) state $\iota$. For this reason we refer to the general idea of naming circumstances explicitly as \emph{nominalization},
even though the examples we discuss are not necessarily actually hybrid logics.

>>>>

\paragraph{Nominalization}
Some classes of assertions benefit specifically from \emph{naming} the explicit conditions where they are true (as opposed to simply requiring them to be true \emph{somewhere} or \emph{everywhere} as in the most classic modal operators).
% This naming generally resembles
% the \emph{satisfaction} operator of 
% \emph{hybrid logic}~\cite{blackburn1995hybrid,areces2001hybrid}: $@_\iota P$ which evaluates the truth of $P$ at the named (Kripke model) state $\iota$. 
Because these named conditions strongly resemble the nominals of hybrid logic,
we refer to the general idea of naming circumstances explicitly as \emph{nominalization},
even though not all of the examples we discuss are actually hybrid logics.
